Forecasting the 2024 US Presidential Election

### 2024-10-22 paper/paper.qmd
Updated the Survey Design portion of the paper.

>>>>

Sampling approach: The sampling approach we will use is stratified random sampling where we divide the population into strata based on.... (age, gender, education level, etc.)
Recruit Respondents: We will recruit respondents using an online survey on Google Forms so that we can minimize the cost and maximize the range of respondents we can reach. We will spend a portion of our budget (specify here) to advertise these surveys and also send out emails, with an additional monetary incentive (specify here) to encourage more participation. 
Data validation: IP address tracking to prevent duplicate responses.
Poll Aggregation: Incorporate Bayesian Inference.

Survey Link: (Short questionnaire asking for demographic questions to be added here)
Copy of Survey:
